---
title: "T-Test Problem"
author: "Kim Godfrey"
date: "Spring, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
Ourdata <- read.csv(file="GSScsv.csv")
```


## Is there a difference in  average years of education (EDUC) between the those who did or did not vote in 2012 (VOTE12)?

$H_O$ : No difference in average years of education between those who voted and those who did vote in 2012

$H_A$ : Yes there is a difference in average years of education between those who voted and those who did not vote in 2012

## graphical summary  

```{r}
plot(EDUC~VOTE12,data=Ourdata)

```


It appears that the average number of years of education is about the same for both groups


## numerical summary

```{r}
favstats(EDUC~VOTE12,data=Ourdata)
```



## inference test



```{r}
t.test(EDUC~VOTE12,data=Ourdata)

```


## conclusion

the p-value from the t-test is 0.005074, this is less than 0.05, so we reject the null hypothesis and conclude we have evidence that there is a difference between the average years of education for those who voted in 2012 and those who did not vote in 2012
